A review on Generative Learning in Computer Vision

### 2020-05-08 paper.tex
updated keywords

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

>>>>

\begin{IEEEkeywords}
generative learning, GAN, autoencoder, computer vision, conditional GAN, progressive GAN, deep convolutional GANs, auxiliary GAN, InfoGANs, 3D-GAN, PacGAN, Pix2PixGAN, Cycle-GAN, Text-to-Image Synthesis (StackGAN), Super-Resolution GAN, Variational Autoencoders
\end{IEEEkeywords}
